\section{Conclusion and Future Work}
\label{sec:conclusion}

\subsection{Summary}
\label{sec:conclusion:summary}

We presented a prototype end-to-end system for cross-language scene
text replacement in video. The system is structured as a five-stage
pipeline that integrates seven machine-learning models---two of
which, a Blur Prediction Network and an Alignment Refiner, we
designed and trained from scratch to address per-frame blur
adaptation and residual tracking error respectively. The other
five components (PaddleOCR, CoTracker3, AnyText2, SRNet, and
Hi-SAM) are pretrained and used through stable interfaces. We
described each stage in detail, including the engineering decisions
made to handle long-to-short translations, interchangeable
background inpainting, and geometric refinement of the canonical
space. Evaluation on real video examples shows the feasibility of
the approach.

\subsection{Model involvement}
\label{sec:conclusion:involvement}

Table~\ref{tab:involvement} summarizes the provenance of each model
in the pipeline, and the nature of our own involvement with it.

\begin{table}[t]
  \centering
  \caption{Models in the pipeline and our involvement with each.}
  \label{tab:involvement}
  \small
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lll}
    \toprule
    Model & Stage & Our involvement \\
    \midrule
    PaddleOCR (PP-OCRv4) & S1 detection       & Pre-trained, used as is \\
    CoTracker3           & S1 tracking        & Pre-trained, used as is \\
    AnyText2             & S3 text editing    & Pre-trained, used as is (Gradio server) \\
    SRNet                & S3/S4/S5 inpainting & Pre-trained, used as is \\
    Hi-SAM               & S3/S4/S5 inpainting & Pre-trained, used as is (default backend) \\
    LCM                  & S4 lighting        & Reimplementation of STRIVE's algorithm \\
    \textbf{BPN}         & S4 blur prediction & \textbf{Trained from scratch} on S2-aligned data \\
    \textbf{Alignment Refiner} & S2 drift correction & \textbf{Designed and trained from scratch} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Positioning}
\label{sec:conclusion:framing}

Section~\ref{sec:exp:discussion} argued that the two paradigms
are complementary rather than competing. We view our specific
contribution as an open, reproducible reference implementation of
the glyph-controlled paradigm: a full pipeline, two compact
networks trained from scratch, and configuration knobs that
expose each module for inspection and extension.

The generative paradigm---Sora~\citep{openai2024sora},
Gen-4~Aleph~\citep{runway2025aleph}, and their successors---
currently achieves superior style preservation and is likely to
dominate the space as glyph control in those systems matures.
Until that happens, modular pipelines like ours offer the
predictable correctness that end-to-end generative models cannot
yet guarantee. An honest positioning of our work is therefore as a
reference implementation of one side of this tradeoff and a
starting point for future hybrid systems, rather than as a direct
competitor.

\subsection{Future work}
\label{sec:conclusion:future}

Several directions follow naturally from the design decisions and
limitations described above.

\begin{itemize}[leftmargin=*]
  \item \textbf{Hybrid generative plus glyph-controlled
    compositing.} The most promising long-term direction: use a
    generative video model for the background and style layer, and
    a glyph-controlled pipeline such as ours for the text layer,
    combining the strengths of both paradigms.
  \item \textbf{Temporal smoothing of the refiner's predictions.}
    The Alignment Refiner currently predicts $\Delta H$ per frame
    independently, leaving small inter-frame micro-oscillations.
    Smoothing over a short temporal window of predicted corner
    offsets is a natural extension.
  \item \textbf{Strengthened rotation signal for the BPN.} The BPN
    tends to predict $\rho \approx 0$ on real data, indicating
    weak signal for rotated blur. Enriching the training
    distribution with oriented blur pairs would improve
    blur-matched compositing for fast-moving subjects.
  \item \textbf{Streaming main pipeline for long videos.} The main
    pipeline currently loads all video frames into memory, which
    limits it to short clips. A streaming architecture already
    exists in our data-generation tool; porting it to the main
    pipeline would lift this limit and extend the system to
    long-form content.
\end{itemize}
